---
title: "Webscrapping Assignment"
author: "Tanvi Arora"
date: "July 8, 2018"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

# load libraries
library(knitr)
library(XML)
library(RCurl)
library(stringr)

# read knitr chunks
read_chunk('Code/HarryPotter.R')

```

## Harry Potter cast
IMDB has listings of full cast members for movies. Get Cast listings for movie - "Harry Potter and the Deathly Hallows: Part 2"
Given URL - [Castings for Harry Potter and the Deathly Hallows: Part 2](http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1.)

#### Data fetch from website

```{r HP_fetchtable}
```


#### Tidying of web data

Dataframe fetched has all the tables from the web page. Cast listings table is the 3rd table. We want to fetch 3rd table and then create a dataframe with only the columns of Actor and Character Names. 
As part of cleanup of data below steps are taken - \
- remove and rows with null/NA data \
- give meaningful column names to the dataframe \
- remove carriage returns or newline from the data \
- replace multiple whitespaces with single whitespace to make it look better. \


```{r HP_cleantable}
```

#### Display Data

Now that we have required data, we want to split Actor Name as FirstName and Surname.

```{r HP_display}
```


## SportsBall