---
title: "Webscrapping Assignment"
author: "Tanvi Arora"
date: "July 8, 2018"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

# load libraries
library(knitr)
library(XML)
library(RCurl)
library(stringr)
library(ggplot2)

# source functions file
source('Code/webextr_functions.R')

# read knitr chunks
read_chunk('Code/HarryPotter.R')
read_chunk('Code/webextr_functions.R')
read_chunk('Code/SportsBall.R')

```

## Harry Potter cast
IMDB has listings of full cast members for movies. Get Cast listings for movie - "Harry Potter and the Deathly Hallows: Part 2"
Given URL - [Castings for Harry Potter and the Deathly Hallows: Part 2](http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1.)

#### Data fetch from website

```{r HP_fetchtable}
```


#### Tidying of web data

Dataframe fetched has all the tables from the web page. Cast listings table is the 3rd table. We want to fetch 3rd table and then create a dataframe with only the columns of Actor and Character Names. 
As part of cleanup of data below steps are taken - \
- remove and rows with null/NA data \
- give meaningful column names to the dataframe \
- remove carriage returns or newline from the data \
- replace multiple whitespaces with single whitespace to make it look better. \


```{r HP_cleantable}
```

#### Display Data

Now that we have required data, we want to split Actor Name as FirstName and Surname.

```{r HP_display}
```


## SportsBall

On the ESPN website, there are statistics of each NBA player. Use data for [San Antonio Spurs](http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs) and fetch data from the **Shooting Statistics** table.

#### Data fetch from website

```{r SB_fetchtable}
```

#### Tidying of web data

Data received has a header record and Totals record. These are not part of the observation and will be removed from the dataset. Header record will be used as column names after renaming some of the columns by sustituting '%' with '_per'. Player column has Player name and his position, these will be seperated into two different columns : Playername and Playerposition.
Data fetched from the website is factor , so we will convert names data to character and all the statistics will be converted to numeric so we can use them for visualization.


```{r SB_cleantable}
```

#### Visualization

Plot a bar chart that shows *Field Goals Percentage Per Game* for each person. 

```{r SB_Plottable}
```
